### 2021-04-05 manuscript.rmd
Further update the manuscript, add abstract, fix language

authornote: |
  The authors would like to thank professor Kasper Welbers (Vrije Universiteit Amsterdam) for his advice on the development of the Dutch dictionary; Dr Junior Yuner Zhu (City University of Hong Kong) for sharing details about her study.
  Source code and data are available at xxxxxx. Prereg: https://osf.io/2h4w8/

abstract: |
  Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

keywords          : "Excepteur sint occaecat cupidatat non proident"
wordcount         : "0"

@@

Comparative content analysis is a frequently used research design in journalism studies. Comparative content analysis is used in modeling journalistic culture [e.g. @esser:2013:C], comparative news value research [e.g. @burggraaff:2017:T;@wilke:2012], news flow research [e.g. @wu:2000:SDI], among others. A comparative content analysis includes news articles from various outlets and usually also from various countries. Then the included news articles are coded either manually or automatically. Although some comparative content analysis studies are purely descriptive, most of these studies are aimed to study how contextual conditions such as characteristics of media outlets (e.g. political orientation, online versus offline) and their countries (e.g. post-communist country) influence the content of news articles. For example, some hypotheses are "the coverage of foreign countries by the news is primarily  determined  by  geographical  proximity  and  the  status  of  the  covered  country" [@wilke:2012, p.306] and "the  degree  of  opinion-orientation  will  be  highest  in  newspapers  from  Polarized  Mediterranean systems and lowest in those from Anglo-American systems." [@esser:2013:C] Employing the language from epidemiology [@susser:1994], the effect on media content in these hypotheses is assumed to be ecological. It assumes a macro contextual factor (e.g. newspapers from Polarized Mediterranean systems) is associated with an outcome at the micro-level (e.g. degree of opinion-orientation [in news articles]).

This study of ecological effect on individual behaviours has a long tradition in social sciences. A famous example was Émile Durkheim’s investigation on the ecological factors associated with suicide. One finding from Durkheim was the higher suicide rate among citizens from Scandinvian countries than those from other European countries. Using today’s standard, Durkheim’s analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative content analysis. An example of hypothesis-generating comparative content analysis is @chan2020combining , in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized. Hypothesis-generating comparative content analysis, however, is rare but has a confirmatory outlook. As we see from the example hypotheses above, most of these studies propose hypotheses to test for ecological effects. Traditional hypothesis testing approaches were used: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries. In @wu:2000:SDI, multiple stepwise regression was used. These approaches are violating the underlying assumptions of the statistical analyses. It highlights the fact that comparative content analysis introduces a feature that researchers usually overlook: media contents are clustered in multilevel: a news article is nested within its media outlet and its media outlet is in turn nested within its country. Such data structure brings two problems: non-atomicity and non-stochasticity.

@@

It is perhaps well-known what ecological fallacy is. We commit ecological fallacy, when we make inference at micro-level (e.g. Eating more chocolate makes one cleverer) based on macro-level data (e.g. the correlation between countries’ chocolate consumption and countries’ number of Nobel winners). The reverse of ecological fallacy, i.e. making inference at macro-level based on micro-level data, is equally fallacious. This fallacy is called atomistic fallacy [@gnaldi:2018:EFC].

@@

This method is the so-called "disaggregation approach". From an epistemic standpoint, searching for ecological effect by studying the value of slope ($\beta_{1}$) leads to atomistic fallacy[@hox2017multilevel]. From a statistical standpoint, this approach violates the underlying independence assumption. Almost all frequentist statistical tests assume that the observations are independent of each other. It is unrealistic to assume articles from the same media outlet are independent: they are subjected to being edited by the same editorial team, to being written by the same group of journalists exposed to the same journalistic culture and paid for by the same employer. Also, the way communication researchers collect their media content resembles cluster sampling rather than random sampling: one usually starts from a specific media outlet and then collects all relevant articles from it. The choice of media outlets or countries are almost always not randomly selected. [^1] This sampling approach makes the independence assumption even more fragile.

@@

[^2]: Some communication researchers apply the disaggregation approach by justifying the intraclass correlation between groups is small and the impact of ignoring the multilevel structure is also small [a finding in @chen:2012:IIL], see an example in @zhu:2020:S [footnote 5]. Even a multilevel modeling textbook avocates this justification [@bickel2007multilevel]. We reject this justification because it violates the independence assumption and thus commits atomistic fallacy. See also @nezlek:2008:IMM for criticism of such justification.

There are two solutions to this. The first solution is to aggregate the micro-level dependent variable across macro-level. Suppose there are $n$ countries in the above example. One can aggregate the total number of articles covering China as $z_{k}$ for the $k$-th country, where $k=i,\ldots,n$. Then, we can do a count-based regression with regression equation like so:

@@

In this equation, $\gamma_{00}$ is the average slope, while $\mu_{0k}$ is group-dependent deviations of the slope from the average. It is usually set as a normal distribution with a variance $\tau_{00}$, i.e. $\mu_{0k} \sim \mathcal{N}(0, \tau_{00})$. Instead of a single value, regression coefficient $\gamma_{00}$ is assumed to be a distribution of values depending on a macro-level group. It addresses the problem of clustering of articles by macro-level variables. This model is called the varying-intercept model and is used frequently in social science research. We can then study the magnitude of $\gamma_{01}$ to determine the ecological effect.

@@

*"Statisticians, like artists, have the bad habit of falling in love with their models."* George E.P. Box (TODO)

@@

We skip elaborating part 1, because some, but certainty not all, researchers have the means to amass a massive amount. The mechanism of how part 2 can be used to derive the likelihood function is beyond the scope of this paper. We provide a tutorial in Appendix I(+++TODO) for those who want to get an intuition. The current standard method, MCMC, is much more computationally intensive and has only been possible on desktop computer since mid-1990s [@robert:2011:SHM]. And only in the last few years that can be done efficiently [@hoffman2014no], thanks to the probablistic programming language *Stan* [@gelman:2015:S]. R interfaces to Stan, such as *brms* [@burkner2017advanced], make Bayesian analysis even more accessible to R users. But still, it is important to be mindful that Bayesian analysis is much more computational intensive than methods such as MLE. Our benchmark suggests that Bayesian analysis needs at least 100 times more running time than MLE.

@@

Also, we excluded media outlets that contributed <1000 articles in that year. This threshold allowed us to retain media outlets that the frequency of China coverage be reliably estimated. In total, 61 media outlets from Spain (n = 11), Romania (n = 11), US (n = 7), Austria (n = 6), Germany (n = 5), Norway (n = 5), Australia (n  = 4), Brazil (n = 4), UK (n = 4), South Korea (n = 2), and the Netherlands (n = 2) were included. These 61 media outlets contributed 1,525,871 articles.

@@

The first test is to increase the number of iterations from 2000 to a higher value, e.g. 4000, and see if the result is consistent with the initial analysis. This check makes sure our result is not some transient result due to short iteration time.

@@

We can use posterior predictive checks to study how our model fits our data. The gist of the method is to use the fitted model to generate some simulated data ($y_{rep}$) and compare them with the original data ($y$). A good model should display a similar probability distribution of $y_{rep}$ and $y$. It can be done with the function *pp_check()* (Figure \@ref(fig:fig3).

@@

The new analysis showed that $\gamma_{01}$ is 0.22 with a 95\% HDI of (0.15 to 0.29) for the year 2020. This analysis displays two things: 1) selection of prior is not always, as many authors have suggested, as controversial and subjective; and 2) Bayesian analysis also makes a strong case for replication studies, the raison d'être of open science [@dienlin:2020:AOS].

>>>>

authornote: |
  The authors would like to thank professor Kasper Welbers (Vrije Universiteit Amsterdam) for his advice on the development of the Dutch dictionary; Dr Junior Yuner Zhu (City University of Hong Kong) for sharing details about her study.
  Source code and data are available at (redacted). Prereg: https://osf.io/2h4w8/

abstract: |
  The purpose of this paper is to argue that researchers should refrain from using current (frequentist) analytical approaches to analyze data from a comparative content analysis. It is because current approaches cannot account for non-atomicity (nested nature) and non-stochasticity (non-random sampling) of the data. Bayesian multilevel regression is suggested to be a, and probably, the only, valid analytical approach. Using the openly available useNews data and the R package brms, we demonstrate how to apply such approach for the analysis of comparative content analysis. We also address common queries of the approach such as choosing the prior distribution and diagnosing the convergence of the model.

keywords          : "Bayesian inference, multilevel model, comparative content analysis, ecological effect"
wordcount         : "0"

@@

Comparative content analysis is a frequently used research design in journalism studies. Comparative content analysis is used in modeling journalistic culture [e.g. @esser:2013:C], comparative news value research [e.g. @burggraaff:2017:T;@wilke:2012], news flow research [e.g. @wu:2000:SDI], among others. A comparative content analysis includes news articles from various outlets and usually also from various countries. Then the included news articles are coded either manually or automatically. Although some comparative content analysis studies are purely descriptive, most of these studies are aimed to study how contextual conditions such as characteristics of media outlets (e.g. political orientation, online versus offline) and their countries (e.g. post-communist country) influence the content of news articles. For example, some hypotheses are "the coverage of foreign countries by the news is primarily  determined  by  geographical  proximity  and  the  status  of  the  covered  country" [@wilke:2012, p.306] and "the  degree  of  opinion-orientation  will  be  highest  in  newspapers  from  Polarized  Mediterranean systems and lowest in those from Anglo-American systems." [@esser:2013:C] Employing the language from epidemiology [@susser:1994], the effect on media content in these hypotheses is assumed to be ecological. It assumes a macro contextual factor (e.g. newspapers from Polarized Mediterranean systems) is associated with an outcome at the micro-level (e.g. degree of opinion-orientation), namely, the article-level.

This study of ecological effect on individual behaviours has a long tradition in social sciences. A famous example was Émile Durkheim’s investigation on the ecological factors associated with suicide. Durkheim found the higher suicide rate among citizens from Scandinvian countries than those from other European countries. Using today’s standard, Durkheim’s analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative content analysis. An example of hypothesis-generating comparative content analysis is @chan2020combining, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized. Hypothesis-generating comparative content analysis, however, is rare. Most studies have a confirmatory outlook. As we see from the example hypotheses above, most of these studies propose hypotheses to test for ecological effects. Traditional (frequentist) hypothesis testing approaches were used: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries. In @wu:2000:SDI, multiple stepwise regression was used. These approaches violate the underlying assumptions of the statistical analyses. It highlights the fact that comparative content analysis introduces a feature that researchers usually overlook: media contents are clustered in multilevel. A news article is nested within its media outlet and its media outlet is in turn nested within its country. Such data structure brings two problems: non-atomicity and non-stochasticity.

@@

It is perhaps well-known what ecological fallacy is. We commit ecological fallacy, when we make inference at micro-level (e.g. Eating more chocolate makes one cleverer) based on macro-level data (e.g. the correlation between countries' chocolate consumption and countries' number of Nobel winners). The reverse of ecological fallacy, i.e. making inference at macro-level based on micro-level data, is equally fallacious. This fallacy is called atomistic fallacy [@gnaldi:2018:EFC].

@@

This method is the so-called "disaggregation approach". From an epistemic standpoint, searching for ecological effect by studying the value of slope ($\beta_{1}$) leads to atomistic fallacy [@hox2017multilevel]. From a statistical standpoint, this approach violates the underlying independence assumption. Almost all frequentist statistical tests assume that the observations are independent of each other. It is unrealistic to assume articles from the same media outlet are independent: they are subjected to being edited by the same editorial team, to being written by the same group of journalists exposed to the same journalistic culture and paid for by the same employer. Also, the way communication researchers collect their media content resembles cluster sampling rather than random sampling: one usually starts from a specific media outlet and then collects all relevant articles from it. The choice of media outlets or countries are almost always not randomly selected. [^1] This sampling approach makes the independence assumption even more fragile.

@@

[^2]: Some communication researchers apply the disaggregation approach by justifying the intraclass correlation between groups is small and the impact of ignoring the multilevel structure is also small [a finding in @chen:2012:IIL], see an example in @zhu:2020:S [footnote 5]. Even a multilevel modeling textbook avocates this justification [@bickel2007multilevel]. We reject this justification because it violates the independence assumption and thus commits atomistic fallacy. See also @nezlek:2008:IMM for a criticism of such justification.

There are two solutions to this. The first solution is to aggregate the micro-level dependent variable across a macro-level inpendent variable. Suppose there are $n$ countries in the above example. One can aggregate the total number of articles covering China as $z_{k}$ for the $k$-th country, where $k=i,\ldots,n$. Then, we can do a count-based regression with a regression equation like so:

@@

In these equations, $\gamma_{00}$ is the average slope, while $\mu_{0k}$ is group-dependent deviations of the slope from the average. It is usually set as having a normal distribution with a variance $\tau_{00}$, i.e. $\mu_{0k} \sim \mathcal{N}(0, \tau_{00})$. Instead of a single value, regression coefficient $\gamma_{00}$ is assumed to be a distribution of values depending on a macro-level group. It addresses the problem of clustering of articles by macro-level variables. This model is called the varying-intercept model and is used frequently in social science research. We can then study the magnitude of $\gamma_{01}$ to determine the ecological effect.

@@

*"Statisticians, like artists, have the bad habit of falling in love with their models."* George E.P. Box

@@

We skip elaborating part 1, because some, but certainty not all, researchers have the means to amass a massive amount. The mechanism of how part 2 can be used to derive the likelihood function is beyond the scope of this paper. <!-- We provide a tutorial in Appendix I(+++TODO) for those who want to get an intuition. --> The current standard method, MCMC, is much more computationally intensive and has only been possible on desktop computer since mid-1990s [@robert:2011:SHM]. And only in the last few years that can be done efficiently [@hoffman2014no], thanks to the probablistic programming language *Stan* [@gelman:2015:S]. R interfaces to Stan, such as *brms* [@burkner2017advanced], make Bayesian analysis even more accessible to R users. But still, it is important to be mindful that Bayesian analysis is much more computational intensive than methods such as MLE. Our benchmark suggests that Bayesian analysis needs at least 100 times more running time than MLE.

@@

We excluded media outlets that contributed <1000 articles in that year. This threshold allowed us to retain media outlets that the frequency of China coverage can be reliably estimated. In total, 61 media outlets from Spain (n = 11), Romania (n = 11), US (n = 7), Austria (n = 6), Germany (n = 5), Norway (n = 5), Australia (n  = 4), Brazil (n = 4), UK (n = 4), South Korea (n = 2), and the Netherlands (n = 2) were included. These 61 media outlets contributed 1,525,871 articles.

@@

The first test is to increase the number of iterations from 2000 to a higher value, e.g. 4000, and see if the result is consistent with the initial analysis. This check makes sure our result is not transient due to short iteration time.

@@

We can use posterior predictive checks to study how our model fits our data. The gist of the method is to use the fitted model to generate some simulated data ($y_{rep}$) and compare them with the original data ($y$). A good model should display a similar probability distribution of $y_{rep}$ and $y$. It can be done with the function *pp_check()* (Figure \@ref(fig:fig3) ).

@@

The new analysis showed that $\gamma_{01}$ is 0.22 with a 95\% HDI of (0.15 to 0.29) for the year 2020. This analysis displays two things: 1) selection of prior is not always, as many authors have suggested, as controversial and subjective; and 2) Bayesian analysis also makes a strong case for replication studies, what open science hopes to enable [@dienlin:2020:AOS].
